学術論文

### 2024-08-18 articles.Rmd
update
update articles

- [45] Toyama, A., Katahira, K., Kunisato, Y. (in press). Examinations of Biases by Model Misspecification and Parameter Reliability of Reinforcement Learning Models. Computational Brain & Behavior

- [44] Hamatani, S., Matsumoto, K., Kunisato, Y., Okawa, S., Yamashita, M., Mizuno, Y. (in press). Dismantling cognitive-behavioral therapy components for attention-deficit hyperactivity disorder in adolescents and adults: protocol for a network meta-analysis. BMJ Open

- [43] Buchanan, E. M., ... Kunisato, Y., ... Primbs, M. (2023). The Psychological Science Accelerator’s COVID-19 rapid-response dataset. Scientific Data, 10, 87.

>>>>

### 2024

- [47] Omizu, T. and Kunisato. Y.(2024). Exploring Effective Intervention Strategies for Depression as a Complex System: Targeted Interventions through Network Simulations. Japanese Psychological Research.

- [46] Kashihara, J., Sugawara, D., Kunisato, Y., Takebayashi, Y., Nakajima, S., Ito, M.(2024). Possible Futures for the Psychological Network Approach: Agenda for Clinical Scientists. Japanese Psychological Research. DOI: https://doi.org/10.1111/jpr.12538

### 2023

- [45] Toyama, A., Katahira, K., Kunisato, Y. (2023). Examinations of Biases by Model Misspecification and Parameter Reliability of Reinforcement Learning Models. Computational Brain & Behavior, 6, 651–670. DOI: https://doi.org/10.1007/s42113-023-00175-4

- [44] Hamatani, S., Matsumoto, K., Kunisato, Y., Okawa, S., Yamashita, M., Mizuno, Y. (2023). Dismantling cognitive-behavioral therapy components for attention-deficit hyperactivity disorder in adolescents and adults: protocol for a network meta-analysis. BMJ Open, 13(4):e068547. DOI: http://dx.doi.org/10.1136/bmjopen-2022-068547

- [43] Buchanan, E. M., ... Kunisato, Y., ... Primbs, M. (2023). The Psychological Science Accelerator’s COVID-19 rapid-response dataset. Scientific Data, 10, 87. DOI: https://doi.org/10.1038/s41597-022-01811-7
